---
title: "Amaznon Prime EDA Report"
fontsize: 10pt
output:
  word_document:
    reference_docx: new_sample_test.docx
    fig_caption: yes
  pdf_document: default
  html_document:
    df_print: paged
geometry: margin= 2cm
params:
  table: some object
always_allow_html: yes
tables: yes
---

```{r, setup, warning=FALSE, echo=FALSE,error=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = params$printcode)
knitr::opts_chunk$set(fig.height=12)
knitr::opts_chunk$set(fig.width=20)
knitr::opts_chunk$set(fig.align='center')


```



```{r, warning=FALSE, echo=FALSE,error=FALSE,message=FALSE}
library(dplyr) # for data wrangling
library(tidytext)
library(mailR)
library(reactable)# for NLP
library(flextable)
library(plotly)
library(stringr) # to deal with strings
library(wordcloud) # to render wordclouds
library(knitr) # for tables
library(DT) # for dynamic tables
library(tidyr)
library(wordcloud2)
library(readr)
library(tinytex)
library(huxtable)
library(tm)
library(ggplot2)
library(shinyhelper)
library(echarts4r)
library(textdata)
library(janeaustenr)
library(dplyr)
library(stringr)
library(reshape2)
library(shiny)
library(modules)
library(dplyr)
library(tidyr)
library(lubridate)
library(dygraphs)
library(sass)
library(glue)
library(ggplot2)
library(RColorBrewer)
library(xts)
library(echarts4r)
library(htmltools)
library(reshape2)


amazon_prime_titles <- read_csv("data/amazon.csv")

amazon_prime_titles  -> amzn

amzn %>% mutate(director =ifelse(is.na(director) == TRUE,"DirJam",director),
                cast =ifelse(is.na(cast) == TRUE,"Tom,Jery",cast),
                country =ifelse(is.na(country) == TRUE,"UKS",country)
) %>% select(-rating,-date_added) -> amzn

amzn[sapply(amzn, is.character)] <- lapply(amzn[sapply(amzn, is.character)], 
                                           as.factor)
amzn %>% arrange(desc(release_year)) -> amzn

```

# Sentiments By Title
<div custom-style=Content>Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book.</div>
```{r warning=FALSE, echo=FALSE,error=FALSE,message=FALSE}

# read.csv("data/sentiment_description.csv",header = T) %>%
#   select(word,sentiment,n) %>% 
#   filter(sentiment == "positive") -> dfsentdescription
      read.csv("data/sentiment_title.csv",header = T) %>% 
        select(word,sentiment,n)-> dfsenttitle



dfsenttitle %>%
  group_by(sentiment) %>%
  slice_max(n, n = 15) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)+
  theme(text = element_text(size=30))

```



\newpage




# Sentiment By Description
<div custom-style=Content>Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book.</div>
```{r warning=FALSE, echo=FALSE,error=FALSE,message=FALSE}

read.csv("data/sentiment_description.csv",header = T)  %>% 
        select(word,sentiment,n)-> dfsentdescription

dfsentdescription %>%
  group_by(sentiment) %>%
  slice_max(n, n = 15) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)+
  theme(text = element_text(size=30))

```



\newpage



# Top 5 Countries With Highest Content
<div custom-style=Content>Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry’s standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book.</div>
```{r warning=FALSE, echo=FALSE,error=FALSE,message=FALSE}
amzn %>% 
      filter(country != "UKS") %>%
      select(country) %>% 
      group_by(country) %>% 
      summarise(Count = n()) %>%
      arrange(desc(Count)) %>% head(5) -> dfq

# Compute percentages
dfq$fraction <- dfq$Count / sum(dfq$Count)

# Compute the cumulative percentages (top of each rectangle)
dfq$ymax <- cumsum(dfq$fraction)

# Compute the bottom of each rectangle
dfq$ymin <- c(0, head(dfq$ymax, n=-1))

# Compute label position
dfq$labelPosition <- (dfq$ymax + dfq$ymin) / 2

# Compute a good label
dfq$label <- paste0(dfq$country, "\n value: ", dfq$Count)


ggplot(dfq, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=country)) +
    geom_rect() +
    geom_text( x=2, aes(y=labelPosition, label=label, color=country), size=6) + # x here controls label position (inner / outer)
    scale_fill_brewer(palette=3) +
    scale_color_brewer(palette=3) +
    coord_polar(theta="y") +
    xlim(c(-1, 4)) +
    theme_void() +
    theme(legend.position = "none")
```

\newpage



# Least 5 Countries With Highest Content
<div custom-style=Content>Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry’s standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book.</div>
```{r warning=FALSE, echo=FALSE,error=FALSE,message=FALSE}
amzn %>% 
      filter(country != "UKS") %>%
      select(country) %>% 
      group_by(country) %>% 
      summarise(Count = n()) %>%
      arrange(desc(Count)) %>% tail(5) -> dfq1

# Compute percentages
dfq1$fraction <- dfq1$Count / sum(dfq1$Count)

# Compute the cumulative percentages (top of each rectangle)
dfq1$ymax <- cumsum(dfq1$fraction)

# Compute the bottom of each rectangle
dfq1$ymin <- c(0, head(dfq1$ymax, n=-1))

# Compute label position
dfq1$labelPosition <- (dfq1$ymax + dfq1$ymin) / 2

# Compute a good label
dfq1$label <- paste0(dfq1$country, "\n value: ", dfq1$Count)


ggplot(dfq1, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=country)) +
    geom_rect() +
    geom_text( x=2, aes(y=labelPosition, label=label, color=country), size=6) + # x here controls label position (inner / outer)
    scale_fill_brewer(palette=1) +
    scale_color_brewer(palette=1) +
    coord_polar(theta="y") +
    xlim(c(-1, 4)) +
    theme_void() +
    theme(legend.position = "none")
```

\newpage

# Store Performance Distribution
<div custom-style=Content>This plot shows the average store rating of all the stores.</div>
```{r warning=FALSE, echo=FALSE,error=FALSE,message=FALSE}

# table_list$store_rating %>%
#       group_by(store_id) %>%
#       summarise(avg = store_rating %>% mean()) %>%
#       mutate(avg = ifelse(store_id == 1, (avg + 2), avg)) %>%
#       mutate(avg = ifelse(store_id == 3, (avg + 1.5), avg)) %>%
#       mutate(avg = ifelse(store_id == 5, (avg + 1), avg)) %>%
#       mutate(avg = ifelse(store_id == 8, (avg + 2), avg)) %>%
#       mutate(store_id = paste0("Store_", store_id)) %>%
#       ggplot(aes(x = store_id %>% factor() %>% fct_reorder(avg),
#                  y = avg,
#                  fill = avg)) +
#       geom_col() +
#       geom_text(aes(label = avg %>% round(1)), nudge_y = 0.5,size=8) +
#       scale_y_continuous(breaks = seq(0,5,0.5)) +
#       coord_flip() +
#       scale_fill_gradient(low = "orange", high = "blue") +
#       theme_minimal() +
#       labs(y = "Average Rating",
#            x = "",
#            fill = "Rating") +
#       theme(
#         axis.text.x = element_text(size=24,angle = 0),
#         axis.text.y = element_text(size=24),
#         axis.title.x = element_text(size=24,face="bold",hjust = 0.5),
#         axis.title.y = element_text(size=24,face="bold",hjust = 0.5,vjust = 0.2),
#         plot.title = element_text(size=24,face="bold",hjust = 0.5,vjust = 0.9),
#         legend.text=element_text(size=24),
#         legend.title=element_text(size=24,face="bold")
# 
#       )
```




\newpage

# Agent Performance
<div custom-style=Content>This plot shows the average rating of all the agents working in stores.</div>
```{r warning=FALSE, echo=FALSE,error=FALSE,message=FALSE}

 amzn %>% head() %>% select(1,2,4)

```




\newpage
# Distribution of Sales on the basis of Store
<div custom-style=Content>This plot shows the Distribution of Sales on the basis of Store.</div>
```{r warning=FALSE, echo=FALSE,error=FALSE,fig.height=20,message=FALSE}

# table_list$gross_income %>% 
#   group_by(store_id) %>% 
#   mutate(store_id = factor(store_id)) %>%
#   mutate(Sales = sales %>% rollmean(k = 7, fill = NA)) %>% 
#   ggplot(aes(x = date,
#              y = Sales,
#              color = store_id)) +
#   geom_line() +
#    facet_wrap(~store_id, ncol = 1, scales = "free_y")+ 
#     theme_minimal()+
#   labs(x="Date")+
#   theme(
#     axis.text.x = element_text(size=24,angle = 0),
#     axis.text.y = element_text(size=24),
#     axis.title.x = element_text(size=24,face="bold",hjust = 0.5),
#     axis.title.y = element_text(size=24,face="bold",hjust = 0.5,vjust = 0.2),
#     plot.title = element_text(size=24,face="bold",hjust = 0.5,vjust = 0.9),
#     legend.text=element_text(size=24),
#     legend.title=element_text(size=24,face="bold"),
#     strip.text = element_text(size = 24,colour = "white"),
#     
#     strip.background = element_rect(
#       color="#ffffff", fill="#000000", size=1.5, linetype="solid"
#     )
#   )

```
